ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-28 pyked.tex
talk -> paper

%====================================================================
\begin{abstract} % not to exceed 200 words
Fundamental experimental measurements of quantities including ignition delay
times, laminar flame speeds, and species profiles serve important roles in
understanding fuel chemistry and validating chemical kinetic models. However,
despite both the importance and abundance of such information in the literature,
the community lacks a widely adopted standard format for this data. This impedes
both sharing and wide use by the community. In this talk, we will introduce a
new Chemical Kinetics Experimental Data format, ChemKED, and the related
Python-based package for creating and validating ChemKED-formatted files called
PyKED. We will also review past and related efforts, and motivate the need for a
new solution. ChemKED currently supports the representation of autoignition
delay time and laminar flame speed measurements. ChemKED-formatted files contain
all of the information needed to simulate experimental data points, including
uncertainty. ChemKED is based on the YAML data serialization language, and is
intended as a human- and machine-readable standard for easy creation and
automated use. Development of ChemKED and PyKED occurs openly on GitHub under
the BSD 3-clause license, and contributions from the community are welcome.
Plans for future development include support for experimental data from jet
stirred reactor, extinction, and speciation measurements.
\end{abstract}

>>>>

%====================================================================
\begin{abstract} % not to exceed 200 words
Fundamental experimental measurements of quantities including ignition delay
times, laminar flame speeds, and species profiles serve important roles in
understanding fuel chemistry and validating chemical kinetic models. However,
despite both the importance and abundance of such information in the literature,
the community lacks a widely adopted standard format for this data. This impedes
both sharing and wide use by the community. In this paper, we will introduce a
new Chemical Kinetics Experimental Data format, ChemKED, and the related
Python-based package for creating and validating ChemKED-formatted files called
PyKED. We will also review past and related efforts, and motivate the need for a
new solution. ChemKED currently supports the representation of autoignition
delay time and laminar flame speed measurements. ChemKED-formatted files contain
all of the information needed to simulate experimental data points, including
uncertainty. ChemKED is based on the YAML data serialization language, and is
intended as a human- and machine-readable standard for easy creation and
automated use. Development of ChemKED and PyKED occurs openly on GitHub under
the BSD 3-clause license, and contributions from the community are welcome.
Plans for future development include support for experimental data from jet
stirred reactor, extinction, and speciation measurements.
\end{abstract}
